\cvsection{TECHNICAL SKILLS}
\cvtag{C}
\cvtag{C++}
\cvtag{Java}
\cvtag{Python}
\cvtag{SQL}
\cvtag{HTML}
\cvtag{JavaScript}
\cvtag{CSS}
\cvtag{Flask}
\cvtag{NumPy}
\cvtag{Pandas}
\cvtag{linux}
\cvtag{git}\\


\textit{Familiar with: } 
\cvtag{Solidity} 
\cvtag{R} 
\cvtag{Unity 3D}
\cvtag{Tensorflow}\\

\cvsection{Projects}

\project{Automatic Multiple Choice Questions Generator}{2020}
\begin{itemize}
\item\justify English reading comprehension MCQs are generated using the deep-learning techniques
for NLP tasks.
\item\justify Mainly focused on generating the distractors. Used LSTM network.
\end{itemize}
\smallskip

\project{Solution for Customer Loyalty problem using Blockchain}{2020}
\begin{itemize}
\item\justify Had used etherum blockchain network to create the smart contract.
\end{itemize}
\smallskip

\project{Dog Bread prediction}{2019}
\begin{itemize}
\item\justify The project was done for the udacity deep learning nanodegree. The model has been
trained using CNN.
\end{itemize}
\smallskip

\project{VR Tour for Kerala Tourism}{2019}
\begin{itemize}
\item\justify It was a VR application which helps in promoting the Kerala Tourisism. Created for
the School of Innovation from Facebook VR Awareness programme 2019
\end{itemize}
\smallskip

\project{Animal Fight}{2019}
\begin{itemize}
\item\justify A animated shooting game build using the Unity3D game engine. It contains 5 variety
of animals as enemy. The goal of the player is to obtain the finishing point with in the
time, without being hurt severely by the enemies.
\end{itemize}
\smallskip

\project{Car Racing}{2018}
\begin{itemize}
\item\justify Racing stimulation build using the Unity3D game engine
\end{itemize}
\smallskip

\project{Maze Game}{2018}
\begin{itemize}
\item\justify A maze game with various levels build using the Unity3D game engine
\end{itemize}
\smallskip

\project{InstaPostDnldr}{2018}
\begin{itemize}
\item\justify A simple implementation which helps to download all the images of an Instagram
profile.Used BeadutifulSoup for scrapping
\end{itemize}
\smallskip



\clearpage





